Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-06 paper/paper.tex
small fixes

The most striking result is the strong growth of the feedback for
$C\ix{high}$ to values higher than 14, while the value for $C\ix{low}$
converges quickly to approximately 1 (FIG. \ref{fig:freq_optimization} (b)).
This behavior may indicate, that the feedback pathway must
overshadow the (maybe too slow) internal mechanics for high frequencies,
while it is the other way round for low frequencies.
Indeed, FIG. \ref{fig:freq_optimization} (a) shows that genotypes with
a lower gain value (on average) are more successful for high frequencies,
which seems to fit in: excessive recurrent dynamics with a long time
scale (compared to the period to be learned) may disturb the learning.
That the single genotypes remain quite scattered throughout the whole
optimization process, though, implies that the exact gain value is not
critical for the success of a genotype.

@@

One can also look at the success of the optimization algorithm in a more
specific way: FIG. \ref{fig:freqrange} shows how well an unoptimized
genotype $G_0$ handles fixed-frequency-challenges when compared to the
genotypes $G\ix{high}$ and $G\ix{low}$ optimized for
$C\ix{high}$ and $C\ix{low}$. Here it becomes clear that $G\ix{high}$ can
indeed succeed at higher frequencies than $G_0$, but that it also fails at
learning lower frequencies -- which was expected. On the contrary, while
the high frequency capacities of $G\ix{low}$ have decreased when compared
to $G_0$, the low frequency capacities have only marginally improved. This
reinforces the impression that the optimization was unable to produce
genotypes that can cope with low frequencies.

>>>>

The most striking result is the strong growth of the feedback for
$C\ix{high}$ to values higher than 14, while the value for $C\ix{low}$
converges quickly to approximately 1 (FIG. \ref{fig:freq_optimization} (b)).
This behavior may indicate that the feedback pathway must
overshadow the (maybe too slow) internal mechanics for high frequencies,
while it is the other way round for low frequencies.
Indeed, FIG. \ref{fig:freq_optimization} (a) shows that genotypes with
a lower gain value (on average) are more successful for high frequencies,
which seems to fit in: excessive recurrent dynamics with a long time
scale (compared to the period to be learned) may disturb the learning.
That the single genotypes remain quite scattered throughout the whole
optimization process, though, implies that the exact gain value is not
critical for the success of a genotype.

@@

One can also look at the success of the optimization algorithm in a more
specific way: FIG. \ref{fig:freqrange} shows how well an unoptimized
genotype $G_0$ handles fixed-frequency challenges when compared to the
genotypes $G\ix{high}$ and $G\ix{low}$ optimized for
$C\ix{high}$ and $C\ix{low}$. Here it becomes clear that $G\ix{high}$ can
indeed succeed at higher frequencies than $G_0$, but that it also fails at
learning lower frequencies -- which was expected. On the contrary, while
the high frequency capacities of $G\ix{low}$ have decreased when compared
to $G_0$, the low frequency capacities have only marginally improved. This
reinforces the impression that the optimization was unable to produce
genotypes that can cope with low frequencies.
